Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-24 paper.tex
Fix economic section

\subsection{Economic}
Piracy, as a theft, also causes real harm to businesses. The act of piracy
does involve stealing and distributing content from creators and organizations
that invested time, money, and effort into the content. In this sense, piracy
is stealing from the individuals' revenue and the government's tax
revenue.~\cite{congress:pirating-the-american-dream}

\blockcquote{mrad:effects-of-ip}[.]{%
  According to Gould and Gruben (1996), IPRs protection stimulates economic
  growth if it is accompanied by a policy of trade liberalization. By
  encouraging initiatives to innovate, IPRs protection may influence the
  economic growth of an open country. Park and Ginarte (1997) found that IPRs
  protection affects economic growth indirectly by stimulating the accumulation
  of factors of production such as physical capital and R\&D capital%
}
Piracy, as proponents of this argument would contend, discourages innovation in
the capitalist marketplace.

>>>>

\subsection{Economic}
Piracy, as a form of theft, is also able to cause real harm to businesses. The
act of piracy can and does involve stealing and distributing content from
creators and organizations that invested time, money, and effort into the
content. In this sense, piracy is stealing from the individuals' revenue and
the government's tax revenue.~\cite{congress:pirating-the-american-dream}

\blockcquote{mrad:effects-of-ip}[.]{%
  According to Gould and Gruben (1996),
  \textins{Intellectual Property Rights (IPRs)} protection stimulates economic
  growth if it is accompanied by a policy of trade liberalization. By
  encouraging initiatives to innovate, IPRs protection may influence the
  economic growth of an open country. Park and Ginarte (1997) found that IPRs
  protection affects economic growth indirectly by stimulating the accumulation
  of factors of production such as physical capital and R\&D capital%
}
Piracy, as proponents of this argument would contend, discourages innovation in
the capitalist marketplace. Conversely, they argue that protecting intellectual
property leads to growth and innovation. Piracy, then, undermines the means for
economic growth that would benefit the general population.
